PGxMine: Text mining for curation of PharmGKB

### 2019-08-05 paper/paper.Rmd
Tidy up of pgxmine name

---
title: "PGxMine: Text mining for curation of PharmGKB"
#output: 
#  bookdown::pdf_document2
#  html_document: 
#    fig_caption: yes
#params:
#   region: east
#editor_options: 
#  chunk_output_type: console
site: bookdown::bookdown_site
documentclass: book
output:
#  bookdown::html_document2
  bookdown::word_document2
#  bookdown::pdf_document2
bibliography: pgmine.bibtex
csl: world-neurosurgery.csl
---

@@

We filtered relations that were scored lower than the previously selected threshold of 0.75 to reduce the false positive rate to create the pgmine_filtered.tsv file. Finally, we collated the results by variant, chemical and where applicable gene IDs to find the total number of papers that discuss each variant/chemical association. This provides a rough metric of the importance of each association and allows a ranking to see which frequently discussed associations should be curated into PharmGKB. This collated version is released as the pgmine_collated.tsv file.

>>>>

---
title: "PGxMine: Text mining for curation of PharmGKB"
#output: 
#  bookdown::pdf_document2
#  html_document: 
#    fig_caption: yes
#params:
#   region: east
#editor_options: 
#  chunk_output_type: console
site: bookdown::bookdown_site
documentclass: book
output:
#  bookdown::html_document2
  bookdown::word_document2
#  bookdown::pdf_document2
bibliography: pgxmine.bibtex
csl: world-neurosurgery.csl
---

@@

We filtered relations that were scored lower than the previously selected threshold of 0.75 to reduce the false positive rate to create the pgxmine_filtered.tsv file. Finally, we collated the results by variant, chemical and where applicable gene IDs to find the total number of papers that discuss each variant/chemical association. This provides a rough metric of the importance of each association and allows a ranking to see which frequently discussed associations should be curated into PharmGKB. This collated version is released as the pgxmine_collated.tsv file.
